---
title: "Consistency tests"
author: 'AA', 'LMM', 'JC', 'AC'
date: "17 de julio de 2018"
output: html_document
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#A. packages and scripts

```{r libraries, scripts, and data}
library(tidyverse)
library(asnipe)
library(igraph)
library(igraphdata)
library(magrittr)
library(geomnet)
library(GGally)
library(readxl)
library(httr)
source('R/cmbDFrame.R')
source('R/exx_calculation.R')
source('R/exy_calculation.R')
source('R/Permutational_community_assortativity.R')
source('R/similarity.function.R')
source('R/getNetworkCommunities.R')
source('R/xy_subsets.R')
source('R/adj_to_edgelist.R')
source('R/rcom_edgeANDgbi.R')
source('R/readxl_online.R')
source('R/batch_linkcomm.R')
source('R/linkcomm_exmod.R')
source('R/batch_linkcomm_exmod.R')
source('R/extended.modularity.R')
```

The following are the data used in [Shizuka et al. (2016)](https://www.sciencedirect.com/science/article/pii/S0003347215004480?via%3Dihub)

##1. Sparrow data (Medium structure)

```{r sparrow data}
sparrow <- read.csv(url('https://datadryad.org/bitstream/handle/10255/dryad.63926/Flock_Season3_Dryad.csv'), na.strings = c('NA', ' ', ''),
                    colClasses = c(rep('factor', 3), rep('character', 10)))

sparrow_raw <- sparrow %>%
    select(-c(1:3)) %>%
    t() %>%
    data.frame() %>%
    gather(key = 'Group', value = 'ID') %>%
    filter(ID != 'NA') %>%
    select(ID, Group) %>%
    get_group_by_individual(data_format = 'individuals')


sparrow_g <- sparrow_raw %>%
    get_network(data_format = "GBI", association_index ="SRI") %>%
    graph.adjacency(mode = "undirected", weighted = TRUE)
```


##2. Tit data (High structure)

```{r tits graph}
data('group_by_individual')

tit_raw <- gbi

colnames(tit_raw) <- paste("N", as.character(seq(1:ncol(tit_raw))), sep = "")

tit_g <- tit_raw %>%
    get_network(data_format = "GBI", association_index ="SRI") %>%
    graph.adjacency(mode = "undirected", weighted = TRUE)

#V(tit_g)$name <- paste("N", as.character(V(tit_g)), sep = "")
```

## 3. Thornbill data (low structure)

```{r thornbill graph}
tho_raw <- read.csv('data/mmc1.csv')

tho_g <- tho_raw %>%
    select(-1) %>%
    get_network(data_format = "GBI", association_index ="SRI") %>%
    graph.adjacency(mode = "undirected", weighted = TRUE)
```

## 4. UK faculty dataset

Nepusz T., Petroczi A., Negyessy L., Bazso F.: Fuzzy communities and the concept of bridgeness in complex networks. Physical Review E 77:016107, 2008. 

```{r}
data('UKfaculty')

uk_g <- UKfaculty %>%
    set.vertex.attribute("name", value = paste("N", 1:81, sep = "")) %>%
    as.undirected(mode = c("collapse"), 
                  edge.attr.comb = igraph_opt("edge.attr.comb"))

uk_raw <- get.edgelist(uk_g) %>%
    data.frame(stringsAsFactors = F) %>% 
    mutate(weights = E(uk_g)$weight) %>% 
    uncount(weights)
```

## 5. Pomatostomus dataset

Rollins LA, Browning LE, Holleley CE, Savage JL, Russell AF, Griffith SC (2012) Building genetic networks using relatedness information: a novel approach for the estimation of dispersal and characterization of group structure in social animals. Molecular Ecology 21(7): 1727-1740. https://doi.org/10.1111/j.1365-294X.2012.05492.x

```{r}
pomatostomus_raw <- read.csv(url('https://datadryad.org/bitstream/handle/10255/dryad.37072/network%20genotype%20file.csv')) %>% 
    select(-c(1:3)) %>% 
    cmbDFrame() %>% 
    use_series(mrgCCombs) %>% 
    data.frame() %>% 
    mutate(X1 = as.character(X1), X2 = as.character(X2))

pomatostomus_g <- pomatostomus_raw %>% 
    as.matrix() %>% 
    graph_from_edgelist(directed = FALSE) %>% 
    simplify(remove.multiple = T, 
                    edge.attr.comb = list(weight="sum", "ignore"))
```



## 6. Hospital encounter network data

P. Vanhems, A. Barrat, C. Cattuto, J.-F. Pinton, N. Khanafer, C. Regis, B.-a. Kim, B. Comte, N. Voirin: Estimating potential infection transmission routes in hospital wards using wearable proximity sensors. PloS One 8(9), e73970 306 (2013). 

```{r}
data(rfid)

rfid_g <- rfid %>% 
    set.vertex.attribute("name", value = paste("N", 1:75, sep = "")) %>%
    as.undirected(mode = c("each"), 
                  edge.attr.comb = igraph_opt("edge.attr.comb"))

E(rfid_g)$weight <- rep(1,length(E(rfid_g)))

rfid_g <- simplify(rfid_g, remove.multiple = T, 
                   edge.attr.comb = list(weight = "sum", "ignore"))

rfid_raw <- get.edgelist(rfid_g) %>% 
    data.frame(stringsAsFactors = F) %>% 
    mutate(weights = E(rfid_g)$weight) %>% 
    uncount(weights)
```

## 7. Enron Email Network 

```{r}
data(enron)

enron_g <- enron %>% 
    set.vertex.attribute("name", value = paste("N", 1:184, sep = "")) %>%
    as.undirected(mode = c("each"), 
                  edge.attr.comb = igraph_opt("edge.attr.comb"))

E(enron_g)$weight <- rep(1,length(E(enron_g)))

enron_g <- simplify(enron_g, remove.multiple = T, 
                    edge.attr.comb = list(weight="sum", "ignore"))

enron_raw <- get.edgelist(enron_g) %>% 
    data.frame(stringsAsFactors = F) %>% 
    mutate(weights = E(enron_g)$weight) %>% 
    uncount(weights)
```

## 8. coral symbiudinum-otu network

Bernasconi, R., Stat, M., Koenders, A. et al. Microb Ecol (2018). https://doi.org/10.1007/s00248-018-1255-4

We projected the network, linking the otu that appear in the same zoox clade.
This data comes from the file 248_2018_1255_MOESM1_ESM.xlsx available as 
supplementary file

```{r}
otu_raw <- read.csv('data/symbio_otu.csv') %>% 
    select(-c(257:262)) %>% 
    rename(bacteria_otu = Bacteria.OTUs.Symbiodinium.types) %>% 
    gather(key = 'zoox', value = 'occurrence', -bacteria_otu) %>% 
    filter(occurrence != 0) %>% 
    uncount(occurrence)

otu_g <- otu_raw %>% 
    graph.data.frame(directed = FALSE)

E(otu_g)$weight <- rep(1,length(E(otu_g)))

otu_g <- simplify(otu_g, remove.multiple = T, 
                    edge.attr.comb = list(weight="sum", "ignore"))

V(otu_g)$type <- V(otu_g)$name %in% otu_raw[,1]

otu_g <- bipartite.projection(otu_g, which = 'false')
```


## 9.AMLC countries collaboration

Ramírez-Ramírez, Rubén D, Montilla, Luis Miguel, Cavada-Blanco, Francoise, & Cróquer, Aldo. (2017). Identification of strengths and weaknesses of cooperative efforts within the wider Caribbean using a network approach [dataset] [Data set]. Zenodo. http://doi.org/10.5281/zenodo.437549

```{r}
amlc_coun_raw <- read.csv(url('https://zenodo.org/record/437549/files/amlc_collaboration_network.csv'), stringsAsFactors = F) %>% 
    select(5, 6) %>% 
    filter(country2 != '')

amlc_coun_raw[amlc_coun_raw == ''] <- 'Unknown'

amlc_coun_g <- amlc_coun_raw %>% 
    graph.data.frame(directed = FALSE)

E(amlc_coun_g)$weight <- 1

E(amlc_coun_g)$weight <- rep(1,length(E(amlc_coun_g)))

amlc_coun_g <- simplify(amlc_coun_g, remove.multiple = T, edge.attr.comb = 'sum')
```


## 10. Karate data

```{r}
karate_raw <-  data(karate) %>% 
    cbind(get.edgelist(karate), E(karate)$weight) %>% 
    data.frame() %>% 
    select(-1) %>% 
    mutate(V4 = as.character(V4)) %>% 
    mutate(V4 = as.numeric(V4)) %>% 
    uncount(V4) %>% 
    rename(V1 = V2, V2 = V3)

data(karate)

karate_g <- karate
```

## 11. Reptile co-presence

Kay GM, Tulloch A, Barton PS, Cunningham SA, Driscoll DA, Lindenmayer DB (2017) Species co-occurrence networks show reptile community reorganization under agricultural transformation. Ecography 41(1): 113-125. https://doi.org/10.1111/ecog.03079

Kay GM, Tulloch A, Barton PS, Cunningham SA, Driscoll DA, Lindenmayer DB (2017) Data from: Species co-occurrence networks show reptile community reorganization under agricultural transformation. Dryad Digital Repository. https://doi.org/10.5061/dryad.3j7f6

```{r}
reptile_raw <- read.csv(url('https://datadryad.org/bitstream/handle/10255/dryad.151384/Dryad_data.csv?sequence=1')) %>% 
    select(-c(1:10)) %>%
    slice(-c(1121:1124)) %>% 
    mutate_all(as.character) %>% 
    mutate_all(as.numeric) 

reptile_raw[reptile_raw > 1] <- 1    

reptile_g <- reptile_raw %>% 
    get_network(data_format = "GBI", association_index ="SRI") %>%
    graph.adjacency(mode = "undirected", weighted = TRUE)
```

## 12. Les miserables networks

```{r}
lesmis_raw <- lesmis$edges %>% 
    data.frame() %>% 
    uncount(degree)

lesmis_g <- lesmis$edges %>% 
    graph.data.frame(directed = FALSE)

E(lesmis_g)$weight <- E(lesmis_g)$degree
```

## 13. Bike sharing network 

```{r}
bikes_raw <- bikes$trips %>% 
    select(-4) %>% 
    uncount(n)

bikes_g <- bikes$trips %>% 
    graph.data.frame(directed = FALSE) %>% 
    simplify(remove.multiple = TRUE, edge.attr.comb = 'sum')

E(bikes_g)$weight <- E(bikes_g)$n
```

##14.  River metacommunities 1

Henriques-Silva R, Logez M, Reynaud N, Tedesco PA, Brosse S, Januchowski-Hartley SR, Oberdorff T, Argillier C (2018) A comprehensive examination of the network position hypothesis across multiple river metacommunities. Ecography, online in advance of print. https://doi.org/10.1111/ecog.03908


Henriques-Silva R, Logez M, Reynaud N, Tedesco PA, Brosse S, Januchowski-Hartley SR, Oberdorff T, Argillier C (2018) Data from: A comprehensive examination of the network position hypothesis across multiple river metacommunities. Dryad Digital Repository. https://doi.org/10.5061/dryad.bp31rm7

```{r}
headwater_raw <- read.delim('data/headwater.txt') %>% 
    select(-c(1:3))


headwater_raw[headwater_raw > 1] <- 1    

headwater_g <- headwater_raw %>% 
    get_network(data_format = "GBI", association_index ="SRI") %>%
    graph.adjacency(mode = "undirected", weighted = TRUE)
```
 
##15.  River metacommunities 2

```{r}
downwater_raw <- read.delim('data/downwater.txt') %>% 
    select(-c(1:3))


downwater_raw[downwater_raw > 1] <- 1    

downwater_g <- downwater_raw %>% 
    get_network(data_format = "GBI", association_index ="SRI") %>%
    graph.adjacency(mode = "undirected", weighted = TRUE)
```

## 16. Alaskan Food web 

Wood SA, Russell R, Hanson D, Williams RJ, Dunne JA (2015) Effects of spatial scale of sampling on food web structure. Ecology and Evolution 5(17): 3769–3782.

```{r}
alaska_raw <- read.csv(url('https://ndownloader.figshare.com/files/6588459')) %>% 
    select(-c(1:5))

alaska_g <- alaska_raw %>% 
    graph.data.frame(directed = FALSE)


E(alaska_g)$weight <- rep(1,length(E(alaska_g)))

alaska_g <- simplify(alaska_g, remove.multiple = T, edge.attr.comb = 'sum')
```

##17. game of thrones network

A. Beveridge and J. Shan, "Network of Thrones," Math Horizons Magazine , Vol. 23, No. 4 (2016), pp. 18-22.

```{r}
got_raw <- read.csv('data/stormofswords.csv') %>% 
    uncount(Weight)

got_g <- read.csv('data/stormofswords.csv') %>% 
    graph.data.frame(directed = FALSE) 
   
E(got_g)$weight <- E(got_g)$Weight
```


## 18. Shipping-boating network

Lacoursière-Roussel A, Bock DG, Cristescu ME, Guichard F, Girard P, Legendre P, McKindsey CW (2012) Disentangling invasion processes in a dynamic shipping-boating network. Molecular Ecology 21(17): 4227-4241. https://doi.org/10.1111/j.1365-294X.2012.05702.x

Lacoursière-Roussel A, McKindsey CW, Bock DG, Cristescu ME, Guichard F, Girard P, Legendre P (2012) Data from: Disentangling invasion processes in a dynamic shipping - boating network. Dryad Digital Repository. https://doi.org/10.5061/dryad.n3v10

```{r}
ship_g <- readxl_online('https://datadryad.org/bitstream/handle/10255/dryad.39629/Boat%20connectivity%20%28updated%29.xls') %>% 
    as.data.frame() %>% 
    column_to_rownames('X__1') %>% 
    mutate_all(as.numeric) %>% 
    mutate_all(funs(replace(., which(is.na(.)), 0))) %>% 
    as.matrix() %>% 
    graph_from_adjacency_matrix(mode = 'undirected', weighted = TRUE) %>% 
    delete.vertices(c('P4', 'M4', 'M21'))

ship_raw <- ship_g 

ship_raw <- ship_g %>% 
    get.edgelist() %>% 
    as.data.frame() %>% 
    mutate(weight = E(ship_g)$weight) %>% 
    uncount(weight)
```

## 19. Pekania network

Bertrand P, Bowman J, Dyer RJ, Manseau M, Wilson PJ (2017) Sex-specific graphs: Relating group-specific topology to demographic and landscape data. Molecular Ecology 26(15): 3898-3912. https://doi.org/10.1111/mec.14174


Bertrand P, Bowman J, Dyer R, Manseau M, Wilson PJ (2017) Data from: Sex-specific graphs: Relating group-specific topology to demographic and landscape data. Dryad Digital Repository. https://doi.org/10.5061/dryad.167d5 

```{r}
pekania_raw <- read.csv(url('https://datadryad.org/bitstream/handle/10255/dryad.143703/FisherGenotypes.csv?sequence=1')) %>% 
    select(-c(1:5)) %>% 
    cmbDFrame() %>% 
    use_series(mrgCCombs) %>% 
    data.frame() %>% 
    mutate(X1 = as.character(X1), X2 = as.character(X2))

pekania_g <- pekania_raw %>% 
    as.matrix() %>% 
    graph_from_edgelist(directed = FALSE) %>% 
    simplify(remove.multiple = T, 
                    edge.attr.comb = list(weight="sum", "ignore"))
```




## 20. Random data

```{r random graph}
set.seed(1)

rnd_raw <- matrix(rbinom(10000, 1, 0.5), ncol=50) %>%
    data.frame()

rnd_g <- rnd_raw %>%
    get_network(data_format = "GBI", association_index ="SRI") %>%
    graph.adjacency(mode = "undirected", weighted = TRUE)
```


#B. Comparison of the results

## Store computationally demanding objects

```{r assortativity and overlapping community calculations}
#run network_assortativity_loop.r
#source('R/Network_assortativity_loop.R')

Results

write.csv(Results, 'output/assortativity_results.csv', row.names = FALSE)

over_comm <- batch_linkcomm('_g')

write.csv(over_comm, 'output/over_comm.csv', row.names = FALSE)
```


```{r}
#test
Results$ExMod <- as.numeric(NA)
for(i in 2:nrow(Results)) {
    linkcomm.object <- eval(parse(text = paste(Results[i, 1], "_g", sep  = ""))) %>% 
    get.edgelist() %>% 
    getLinkCommunities(plot = FALSE)
    
    if(linkcomm.object$numbers[3] < 3) next()
    
    Results$ExMod[i] <- max(linkcomm.exmod(linkcomm.object))
    print(i)
}

#then, finish writing batch_linkcomm_exmod
```

```{r restore computationally demanding objects}
over_comm <- read.csv('output/over_comm.csv')

metrics <- read.csv('output/assortativity_results.csv') %>% 
    rename(network = Data) %>% 
    bind_cols(over_comm) %>% 
    select(-network1)
```

Comparacion con metricas para comunidades discretas

```{r overlapping comms}
ggpairs(metrics[,-c(1,5,6)])
#ggpairs(metrics[metrics$Ascanio_perm != 0,-c(1,5,6)])
```
